\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-23 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
changement papier fin + OA en cours

The paper compares the empirical performances of two models: one with only ad-valorem costs (Model (A)) and one with where both ad-valorem and additive costs (Model (B)).
For comparison purposes, we also estimate the model with only additive costs (Model (C)), in which case the estimated equation is:
$$\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}\right) + \epsilon^{add}_{ik}$$

@@

Results for Models (A) and (B) are identical to those reported in the paper. Unsurprisingly, the estimated size of overall transport costs under Model (C) is of same order of magnitude as in Models (A) and (B). We also observe a downward trend of transport costs over time, in particular since 1980.\\

@@

To go further into the comparison of the empirical relevance of our three empirical models (A), (B) and (C), we compare quality of fit diagnostic tests in this section. Table \ref{tab:3models_diagnosis_air} reports the results for air transport, and Table \ref{tab:3models_diagnosis_vessel} those for vessel transport. In both tables, we report the values of the $R^2$, the Standard Error of Regression (SER), the AIC criterion  and the log-likelihood (LL) value. We also report the value of the log-likelihood ratio that tests the quality of fit of the global model (Model (B)) compared to the other two models.

@@

For all years and whatever the transport mode considered, the model with additive costs only (Model (C)) is consistently dominated (in terms of quality of fit properties) by the model with multiplicative costs only (Model (A)), which is itself consistently dominated by the complete model (Model (B)), whatever the type of diagnostic test considered. That justifies our choice to disregard Model (C) in the main text.

@@

In this section, we report the estimation results when we retain the 4-digit classification level ($s$=4-digit).

@@

Tables \ref{tab:result_air_rob} and \ref{tab:result_ves_rob} report the estimates of both models (with and without additive costs) in air and vessel transport respectively. Estimates at the 4-digit level confirm the significant role of the additive component in fitting international transport costs we found at the 3-digit level.

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, selected years, 4-digit level}
\begin{center}
  \footnotesize{
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (A)} ($\widehat{\tau}^{ice}-1$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 5.2 & 4.4 & 4.1 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B)}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term }($\widehat{\tau}^{adv}-1$, in \%) }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term} ($\widehat{t}/\widetilde{p}$), in \%}    \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{10cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs.
Statistics are obtained weighting each observation by its share in trade (mode-dependent).
Additive term expressed in fraction of fas price.}}}
\end{tabular}%
}
\end{center}
  \label{tab:result_air_rob}
\end{table}%

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Air: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_air_rob}%
		\input{TableB1_air.tex}
		\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}%

\begin{table}[htbp]
  \centering
\caption{Vessel: Transport costs estimates, selected years, 4-digit level}
\begin{center}
  \footnotesize{
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\
\hline
\multicolumn{7}{l}{\textbf{Model (A)} ($\widehat{\tau}^{ice}-1$, in \%)} \\
\hline
Mean  & 9.8 & 6.1 & 5.8 & 5.1 & 4.2 & 3.6  \\
Median & 9.4 & 5.1 & 4.8 & 4.5 & 3.8 & 3.1 \\
%Standard Error & 0.060 & 0.038 & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.030} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.020} \\
\hline
\multicolumn{7}{l}{\textbf{Model (B)} }\\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term} ($\widehat{\tau}^{adv}-1$, in \%) }   \\ \hline
Mean  & 5.4 & 3.4 & 2.8 & 2.8 & 2.4 & 2.1  \\
Median & 4.9 & 3.0 & 2.4 & 2.5 & 2.6 & 1.8 \\
%Standard Error & 0.043 & 0.026 & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.016} & \multicolumn{1}{c}{0.013}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term} ($\widehat{t}^{add}/\widetilde{p}$, in \%) }   \\ \hline
Mean  & 4.6 & 2.6 & 3.1 & 2.4 & 2.1 & 1.5  \\
Median & 2.9 & 1.3 & 1.9 & 1.5 & 1.3 & 0.8 \\
%Standard Error & 0.068 & 0.044 & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.023} \\
\hline
\# observations & 19196 & 17916 & \multicolumn{1}{c}{29387} & \multicolumn{1}{c}{36677} & \multicolumn{1}{c}{37643} & \multicolumn{1}{c}{38820} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{10cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs.
Statistics are obtained weighting each observation by its share in trade (mode-dependent).
Additive term expressed in fraction of fas price.}}}
\end{tabular}%
}
\end{center}
\label{tab:result_ves_rob}%
\end{table}%

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_air_rob}%
		\input{TableB1_ves.tex}
		\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Air: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_air_rob}%
%\vspace{0.5cm}
%\scalebox{0.97}{
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}              \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\
\hline
\multicolumn{7}{l}{\textbf{R$^2$}}      \\ \hline
Model (A)& \multicolumn{1}{c}{0.48} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.35} \\
Model (B) & \multicolumn{1}{c}{0.63} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{0.45} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }  \\ \hline
Model (A)& \multicolumn{1}{c}{0.8} & \multicolumn{1}{c}{0.9} & \multicolumn{1}{c}{0.83} &   0.87    & \multicolumn{1}{c}{0.88} & \multicolumn{1}{c}{0.93}  \\
Model (B) & \multicolumn{1}{c}{0.67} & \multicolumn{1}{c}{0.74} & \multicolumn{1}{c}{0.69} &  0.80     & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.86}  \\
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (A) & \multicolumn{1}{c}{-17505.6} & \multicolumn{1}{c}{-21813.5} & \multicolumn{1}{c}{-30960.6} & \multicolumn{1}{c}{-44067.6} & \multicolumn{1}{c}{-49375.6} & \multicolumn{1}{c}{-53197.9}  \\
Model (B) & \multicolumn{1}{c}{-14895.8} & \multicolumn{1}{c}{-18589.9} & \multicolumn{1}{c}{-26553.5} & \multicolumn{1}{c}{-37297.9} & \multicolumn{1}{c}{-45747.6} & \multicolumn{1}{c}{-49899.1}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} }  \\ \hline
Model (A)& \multicolumn{1}{c}{36243.1} & \multicolumn{1}{c}{44966.9} & \multicolumn{1}{c}{63417.1} & \multicolumn{1}{c}{89747.2} & \multicolumn{1}{c}{100317.13} & \multicolumn{1}{c}{107963.7} \\
Model (B) & \multicolumn{1}{c}{31873.6} & \multicolumn{1}{c}{39495.8} & \multicolumn{1}{c}{55777.1} & \multicolumn{1}{c}{77439.9} & \multicolumn{1}{c}{94059.1} & \multicolumn{1}{c}{102224.3}  \\ \hline
\multicolumn{7}{l}{\textbf{Test LL} }    \\ \hline
Stat LL ratio (B vs A) & \multicolumn{1}{c}{5219.5} & \multicolumn{1}{c}{6447.1} & \multicolumn{1}{c}{8814.1} & \multicolumn{1}{c}{13539.4} & \multicolumn{1}{c}{7256.0} & \multicolumn{1}{c}{6597.5}  \\
\# of restrictions (B vs A) & \multicolumn{1}{c}{640} & \multicolumn{1}{c}{698} & \multicolumn{1}{c}{778} & \multicolumn{1}{c}{833} & \multicolumn{1}{c}{824} & \multicolumn{1}{c}{818}  \\
p-value (B vs A) & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.00} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (A) = with only ad-valorem transport costs.
Model (B) = with additive \& ad-valorem transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Air: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_air_rob}%
		\input{TableB3_air.tex}
		\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Vessel: Measures of goodness of fit, 4-digit level}
\begin{center}
\label{tab:good_fit_ves_rob}%
  \footnotesize{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}                   \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\ \hline
\multicolumn{7}{l}{\textbf{R$^{2}$}} \\ \hline
Model (A) & 0.50  & 0.45  & \multicolumn{1}{c}{0.47} & \multicolumn{1}{c}{0.41} & \multicolumn{1}{c}{0.37} & \multicolumn{1}{c}{0.35} \\
Model (B) & 0.66  & 0.62  & \multicolumn{1}{c}{0.62} & \multicolumn{1}{c}{0.58} & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.46} \\ \hline
\multicolumn{7}{l}{\textbf{SER} }\\ \hline
Model (A) &    0.58   &   0.64    & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.0.72} & \multicolumn{1}{c}{0.79} & \multicolumn{1}{c}{0.82} \\
Model (B) &   0.48    &    0.53   & \multicolumn{1}{c}{0.51} & \multicolumn{1}{c}{0.61} & \multicolumn{1}{c}{0.69} & \multicolumn{1}{c}{0.75} \\ \hline
\multicolumn{7}{l}{\textbf{Log-likelihood} } \\ \hline
Model (A)& -16460.1 & -16951.6 & \multicolumn{1}{c}{-26771.4} & \multicolumn{1}{c}{-39008.3} & \multicolumn{1}{c}{-43888.9} & \multicolumn{1}{c}{-47161.6} \\
Model (B) & -12743.65 & -13546.9 & \multicolumn{1}{c}{-21752.8} & \multicolumn{1}{c}{-33281.0} & \multicolumn{1}{c}{-39078.9} & \multicolumn{1}{c}{-43399.2}  \\ \hline
\multicolumn{7}{l}{\textbf{AIC criteria} } \\ \hline
Model (A) & 34464.2 & 35491.2 & \multicolumn{1}{c}{55272.9} & \multicolumn{1}{c}{79800.7} & \multicolumn{1}{c}{89459.8} & \multicolumn{1}{c}{95987.2}\\
Model (B) & 28271.3 & 29877.8 & \multicolumn{1}{c}{46595.6} & \multicolumn{1}{c}{69743.9} & \multicolumn{1}{c}{81155.7} & \multicolumn{1}{c}{89692.4} \\ \hline
\multicolumn{7}{l}{\textbf{Test LL}} \\ \hline
Stat LL ratio (B vs A) & 12385.80 & 11226.8 & \multicolumn{1}{c}{17354.7} & \multicolumn{1}{c}{20113.5} & \multicolumn{1}{c}{16608.2} & \multicolumn{1}{c}{12589.6} \\
\# of restrictions (B vs A) & 797   & 814   & \multicolumn{1}{c}{881} & \multicolumn{1}{c}{910} & \multicolumn{1}{c}{886} & \multicolumn{1}{c}{874} \\
p-value (B vs A) & 0.000 & 0.000 & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{13cm}{ \vspace{7pt}\scriptsize{Notes: Model (A) = with only ad-valorem transport costs.
Model (B) = with additive \& ad-valorem transport costs.
$R^{2}$ between the log of predicted ratio and the log of the observed ratio.
The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of products.}}}
\end{tabular}%
}
\end{center}
\end{table}%

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_air_rob}%
		\input{TableB3_ves.tex}
		\begin{tablenotes}
			\tiny
			\item Statistics are weighted by value
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
	\end{table}

@@

As mentioned in the paper, the estimates for air transport costs in 1989 show a surprisingly high value for the additive component (the additive cost is estimated to amount to $4.6\%$ of the export price, whereas it amounts to 2.5\% on average between 1974 and 1988, and to 1.7\% over the following decade 1990-2000). This can be attributed to the presence of outliers in the distribution of the additive costs estimates, despite the exclusion of outliers in the data. The maximum value for $\widehat{t}/\widetilde{p}$ is 10,000\% in 1989, whereas it amounts to 1,690\% on average over 1974-1988 and to 1,500\% on average over 1990-2000. Accordingly, in the paper we discard this year 1989 when we report the average values over the period of the transport costs estimates in air transport.\\
Excluding or excluding a single year out of 45 does not make much difference in the weighted mean transport cost.
%When 1989 is included, the weighted mean transport cost value amounts to 1.9\% for the ad-valorem component, vs 1.8\% when 1989 is excluded. The weighted median value is left unchanged at 2.9\% whether 1989 is included or not.

@@

In this section, we provide a variance decomposition exercise on the observed cif-fas price gap.
Specifically, we determine the share of the observed variance in the ratio $\ln(\frac{p_{ik}}{\widetilde{p}_{ik}}-1)$ that comes from \textit{i)} the between-product variance (at the 5-digit level, $k$) and \textit{ii)} the between-sector variance (at the 3-digit level, $s$).
The variance decomposition expression at the product level $k$ (5-digit level) is obtained by applying the following formula (by year and transport mode):

@@

In this section, we explore an alternative estimation method, which proceeds as follows. $\beta$ can be separately estimated for each industry $s$-origin country $i$ using the following regression:

@@

where $d$ denotes the US district of entry and $k$ denotes an HS-10 product, $TC_{ikd}$ being the transport costs and $Z$ a set of controls variables. The identification of $\beta_{is}$, in this case, relies on exploiting the variability between sub-sectors at the 10-digit
level ($k$) and between ports of entry in the US ($d$). From this, one can then recover the levels of additive and multiplicative transports costs. Denoting $\widehat{\beta}_{is(k)}$ the estimated $\beta$ for a given sector-country $i,s(k)$, one can indeed solve the following two-equation system:

@@

With respect to the trade flows coverage, the method is run country by country, and 3-digit sector by 3-digit sector, exploiting the variability within each country-3d sector across 10-d sub-sectors and ports of entry. Yet, it appears that for many pairs (country, 3-digit sector), there is too few variability across sub-sectors or ports en entry given the number of fixed effects included in the regression, to estimate the equation.. This can be seen comparing the number of observations by year/ transport mode between this alternative method and our baseline method reported in Table \ref{tab_comp_referee1_baseline}. Put differently, this methodology discards countries which export a limited range of goods to the US and/or which arrive in the USA through the same ports of entry. In this respect, the induced selection bias reduces the general scope of the transport costs estimates.

@@

If we take the value of the $\beta$ by itself, there is no clear criteria to discriminate between the value estimated with the baseline method and estimating directly $\beta$ (when, of course, run on the same sample).
Further, as shown in Table \ref{tab_comp_referee1_baseline}, there is no clear sign of a potential upwards or downwards bias that would be attached to either method.
Things are more clear-cut in terms of accuracy of the estimation. Specifically, the baseline method yields a more precise estimation of the $\beta$ than the direct method. To develop on this, for each year and transport mode:
\begin{itemize}
	\item The direct method estimates one value for the share of additive component $\beta$ at the $i,s$ level denoted $\hat{\beta}^{dir}_{is(k)}$ associated with a standard deviation $SD_{is}$, by year and transport mode. From this, we can compute the size of the 5-95\% confidence interval $CI^{dir}_{is} = \hat{\beta}_{is}^{max,dir} - \hat{\beta}_{is}^{min,dir}$ where:
	$$\hat{\beta}_{is}^{min,dir} = \hat{\beta}^{dir}_{is(k)} - 1.96 SD_{is},\quad \hat{\beta}_{is}^{max,dir} = \hat{\beta}^{dir}_{is(k)} + 1.96 SD_{is}$$

	\item  The baseline method estimates the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We compute the accuracy of the $\beta$ estimation through a bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of trade costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 confidence interval for each couple $i,s$. Writing $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the size of the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the direct method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

@@

One explanation of the limited accuracy of the alternative method might be the following. Given that the estimation method is run at the country-sector level (exploiting heterogeneity \textit{within} a given country-sector pair), it implicitly assumes that transport costs are independent \textit{across} sectors and \textit{across} origin countries. Put in plain words, it assumes that transport costs of say, cars, have nothing in common whether those goods comes from France or from Germany; or that transport costs that apply to imported goods from France have no common component across sectors. This is a disputable assumption. From a statistical point of view, it implies leaving aside information contained in the fact that transport costs have a both a country-specific component and a sector-specific component. We believe that explains the better accuracy of our baseline estimation.

\subsubsection{Weights and quantities}

>>>>

The paper compares the empirical performances of two models: one with only ad-valorem costs (Model (A)) and one with where both ad-valorem and additive costs (Model (B)).
For comparison purposes, we also estimate a third model with only additive costs (Model (C)), in which case the estimated equation is:
$$\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\frac{t_{i} + t_{s(k)}}{\widetilde{p}_{ik}}\right) + \epsilon^{add}_{ik}$$

@@

Results for Models (A) and (B) are identical to those reported in the paper. Unsurprisingly, the estimated size of overall transport costs under Model (C) is of same magnitude as in Models (A) and (B). We also observe a downward trend of transport costs over time, in particular since 1980.\\

@@

To go further into the comparison of the empirical relevance of our three empirical models, we compare quality of fit diagnostic tests. Table \ref{tab:3models_diagnosis_air} reports the results for air transport, and Table \ref{tab:3models_diagnosis_vessel} those for vessel transport. In both tables, we report the values of the $R^2$, the Standard Error of Regression (SER), the AIC criterion  and the log-likelihood (LL) value. We also report the value of the log-likelihood ratio that tests the quality of fit of the global model (Model (B)) compared to the other two models.

@@

For all years and whatever the transport mode considered, the model with additive costs only (Model (C)) is consistently dominated (in terms of quality of fit properties) by the model with multiplicative costs only (Model (A)), which is itself consistently dominated by the complete model (Model (B)). This conclusion holds whatever the type of diagnostic test considered. That justifies our choice to disregard Model (C) in the main text.

@@

In this section, we report the estimation results when we retain a sectorial classification at the 4-digit level ($s$=4-digit).

@@

Tables \ref{tab:result_air_rob} and \ref{tab:result_ves_rob} report the estimates of both models (with and without additive costs) in air and vessel transport respectively. Estimates at the 4-digit level confirm the significant role of the additive component in fitting international transport costs that we found at the 3-digit level.

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Air: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_air_rob}%
		\input{TableB1_air_reshaped.tex}
		\begin{tablenotes}
			\scriptsize
			\item Statistics are obtained weighting each observation by its share in trade (mode-dependent).
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}%

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Transport costs estimates, selected years, 4-digit level}
		\label{tab:result_air_rob}%
		\input{TableB1_ves_reshaped.tex}
		\begin{tablenotes}
			\scriptsize
			\item Statistics are obtained weighting each observation by its share in trade (mode-dependent).
			\item \textbf{Model (A): Ad-valorem transport costs only}
			\item \textbf{Model (B): With additive and ad-valorem transport costs}
		\end{tablenotes}
\end{table}

@@

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Air: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_air_rob}%
		\input{TableB3_air_reshaped.tex}
{\parbox[l]{12cm}{
			\scriptsize{Notes: Model (A) = with only ad-valorem transport costs. Model (B) = with additive \& ad-valorem transport costs. $R^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of sectors. }}}
\end{table}

\begin{table}[htbp]
	\centering
%	\footnotesize{
		\caption{Vessel: Measures of goodness of fit, 4-digit level}
		\label{tab:good_fit_air_rob}%
		\input{TableB3_ves_reshaped.tex}
		%\begin{tablenotes}
{\parbox[l]{12cm}{
			\scriptsize{ Notes: Model (A) = with only ad-valorem transport costs. Model (B) = with additive \& ad-valorem transport costs. $R^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e. the number of partner countries plus the number of sectors. }}}
		%\end{tablenotes}
	\end{table}

@@

As it can be inferred from Table \ref{tab_oa:result_air_ally3}, the estimates for air transport costs in 1989 show a surprisingly high value for the additive component (the additive cost is estimated to amount to $4.6\%$ of the export price, whereas it amounts to 2.5\% on average between 1974 and 1988, and to 1.7\% over the following decade 1990-2000). This can be attributed to the presence of outliers in the distribution of the additive costs estimates, despite the exclusion of outliers in the data. The maximum value for $\widehat{t}/\widetilde{p}$ is 10,000\% in 1989, whereas it amounts to 1,690\% on average over 1974-1988 and to 1,500\% on average over 1990-2000. Accordingly, in the paper we discard this year 1989 when we report the average values over the period of the transport costs estimates in air transport, all the more as excluding or not excluding a single year out of 45 ones does not make much difference in the weighted mean transport cost.

@@

In this section, we provide a variance decomposition exercise on the observed cif-fas price gap.
Specifically, we determine the share of the observed variance in the ratio $\ln(\frac{p_{ik}}{\widetilde{p}_{ik}}-1)$ that comes from \textit{i)} the between-product variance (at the 5-digit level, $k$) and \textit{ii)} the between-sector variance (at the 3-digit level, $s$).
The variance decomposition expression at the product level $k$ is obtained by applying the following formula (by year and transport mode):

@@

In this section, we explore an alternative estimation method (so called ``direct method'' for sake of clarity), which proceeds as follows. $\beta$ can be separately estimated for each sector $s$-origin country $i$ using the following regression:

@@

\noindent where $d$ denotes the US district of entry and $k$ denotes an HS-10 product, $TC_{ikd}$ being the transport costs and $Z$ a set of controls variables. The identification of $\beta_{is}$, in this case, relies on exploiting the variability between products at the 10-digit
level ($k$) and between ports of entry in the US ($d$). From this, one can then recover the levels of additive and multiplicative transports costs. Denoting $\widehat{\beta}_{is(k)}$ the estimated $\beta$ for a given sector-country $i,s(k)$, one can indeed solve the following two-equation system:

@@

With respect to the trade flows coverage, the method is run country by country, and 3-digit sector by 3-digit sector, exploiting the variability within each country-3d sector across 10-d sub-sectors and ports of entry. Yet, it appears that for many pairs (country, 3-digit sector), there is too few variability across sub-sectors or ports en entry given the number of fixed effects included in the regression, to estimate the equation. This can be seen comparing the number of observations by year/ transport mode between this alternative method and our baseline method reported in Table \ref{tab_comp_referee1_baseline}. Put differently, this methodology discards countries which export a limited range of goods to the US and/or which arrive in the USA through the same ports of entry. In this respect, the induced selection bias reduces the general scope of the transport costs estimates.

@@

If we take the value of $\beta$ by itself, there is no clear criteria to discriminate between the value estimated with the baseline method and estimating directly $\beta$ (when, of course, run on the same sample).
Further, as shown in Table \ref{tab_comp_referee1_baseline}, there is no clear sign of a potential upwards or downwards bias that would be attached to either method.

Things are more clear-cut in terms of accuracy of the estimation. Specifically, we show that the baseline method yields a more precise estimation of the $\beta$ than the direct method. We reach this conclusion by implementing the following steps, for each year and transport mode.
\begin{itemize}
	\item The direct method estimates one value for the share of additive component $\beta$ at the $i,s$ level denoted $\hat{\beta}^{dir}_{is(k)}$ associated with a standard deviation $SD_{is}$, by year and transport mode (where the subscript $^{dir}$ identifies the direct method). From this, we can compute the size of the 5-95\% confidence interval $CI^{dir}_{is} = \hat{\beta}_{is}^{max,dir} - \hat{\beta}_{is}^{min,dir}$ where:
	$$\hat{\beta}_{is}^{min,dir} = \hat{\beta}^{dir}_{is(k)} - 1.96 SD_{is},\quad \hat{\beta}_{is}^{max,dir} = \hat{\beta}^{dir}_{is(k)} + 1.96 SD_{is}$$

	\item  The baseline method estimates the underlying trade costs components ($\widehat{\tau}_i$, $\widehat{\tau}_s$, $\widehat{t}_i$, $\widehat{t}_s$) with an associated matrix of variance-covariance, from which we can rebuild $\beta_{is}$ (on a year-transport mode basis). As such, it does not yield an estimate of $\beta_{is}$ and an associated standard deviation, so that we cannot directly compare the precision of the estimation. We hence compute the accuracy of the $\beta$ estimation through a bootstrap method. Specifically, on a yearly/mode basis we draw a distribution of transport costs components and associated $\beta_{is}$ (10,000 random draws) from which we can compute the mean, the median and the 5-95 confidence interval for each couple $i,s$. Denoting $\beta_{is}^{95}$ and $\beta_{is}^{05}$ the associated thresholds, we then obtain the size of the confidence interval $CI_{is}= \beta_{is}^{95}- \beta_{is}^{05}$.\footnote{Notice that this should be made on the same sample as the one obtained with the direct method, since the goal is to compare the accuracy of the $\beta_{is}$ estimate - implying to have the same sample of countries / sectors at first. }

@@

One explanation of the limited accuracy of the alternative method might be the following. Given that the estimation method is run at the country-sector level (exploiting heterogeneity \textit{within} a given country-sector pair), it implicitly assumes that transport costs are independent \textit{across} sectors and \textit{across} origin countries. Put in plain words, it assumes that transport costs of say, cars, have nothing in common whether those goods comes from France or from Germany; or that transport costs that apply to imported goods from France have no common component across sectors. This is a disputable assumption. From a statistical point of view, it implies leaving aside information contained in the fact that transport costs have a both a country-specific component and a sector-specific component. We believe that this explains the better accuracy of our baseline estimation.

\textbf{XXX Lise stop here relecture XXX }
\subsubsection{Weights and quantities}
